### 2015-06-04 LOI/inc2.tex
LOI..

\underline{\textbf{Executive Summary:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.

Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights into
mission critical scientific processes in exascale computing.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Cepth.

%
We will also study ??
%
Finally, we will, jointly with application partners, study the behvior of how data gets written and read from the storage layers, and
what key inishgts can be used in the next generation LCF systems, along with future exascale systems.

\underline{\textbf{Key Technical Contribution:}} The primary contribution of
our research are insights into how to build a hiearchical organization and storage
of massive scientific data sets generated from exascale computations along with 
the necessary information needed for advanced data validation and exploration from 
experimental and observational data. 
We are fundamentally trying to address the fundmantal questions : 1)  How can we 
place and mangage massive scienfici data across all of the tiers of the storage and memory
hiearchy? 2) What are the proper semantics needed in order to help bring knowledge from the applications
to the middleware layer. 3) What information from the storage layer can be exposed to the middleweare such
that the placement of information can be agreed upon from what the application requires and what the
system resources are available.

>>>>

{\bf Title of Pre-application:} Hierarchal Extreme Scale Knowledge Management \par
{\bf Principal Investigator:} Scott Klasky, Group Leader, ORNL, 854-241-9980, klasky@ornl.gov \par
{\bf Funding Opportunity Announcement Number: DE-FOA-0001338} \par
{\bf List of all co-PIs and Key/Senior Personnel} \par
Hasan Abbasi, Oak Ridge National Laboratory \par
Mark Ainsworth, Oak Ridge National Laboratory JFA, Brown University \par
Matthew Curry, Sandia National Laboratory\par
Qing Liu, Oak Ridge National Laboratory \par
Jay Lofstead, Sandia National Laboratory \par
Kimmy Mu, Oak Ridge National Laboratory \par
Carlos Malzahn, U. Cal. Santa Cruz \par
Manish Parashar, Rutgers University, Oak Ridge National Laboratory \par
 Sudharshan Vazhkudai, Oak Ridge National Laboratory \par
Lee Ward, Sandia National Laboratory \par
\vskip 0.2 in

\underline{\textbf{Objectives:}} Exascale scientific discovery will
introduce more complex hardware, and many simulations will be bottlenecked 
without sufficient new research into manging and storing the large data which will be
produced during the simulation, and analzyed for months after the simulations.
Our goal is to explore and address
the multi-tier challenges that are faced by scientists in creating and
managing and storing their data  to expedite insights into
mission critical scientific processes in exascale computing.
%
We propose a research program that aims to explore a hiearchical organization and storage infstraturure which will facilitiate 
how we data can be written and read efficiently. In order to help us explore our many research issues, we will build upon the
sucess of our middleware system, ADIOS, our multi-tier storage system, Sirocco, and our distributed storage system, Cepth.
We will also take advantage of our staging system, Data Spaces, and our Comon communication Interface (CCI) and build on all of
our sucessful software used in petascale simulations to understand the new directions which need to be understood to fully develop
the next generation I/O and Storage System for exascale and beyond systems.

%
We will apply a technique which will re-organize and possibly reduce the total amount of information based on user intentions along
with direct feedback from the storage and I/O system to allow data to be optimized not just for output, but also for many of the complex
reading patterns. Since data analysis and visualization will be performed in both an in situ and post processing environment, 
we will continue to use our I/O and storage abstractions to help enable applications to take full advantage of the hardware and softare 
environments. Because data volumes are strictly outstripping available bandwidths, compression will
be required. Rather than focusing solely on lossless compression, we will
incorporate lossy compression with the ability to annotate data allowing
optimized algorithm selection based on the numerical methods employed in the
source simulation. We plan to epxlore this tradeoff of storage capacity and
bandwidth for computation to determine how to offer the user options that can
meet their needs with desireable performance characteristics.
%
Our objective is to reduce the time to knowledge, which means that we will also support additional access modes, beyond the traditional 
Checkpoint/Restart methods, and understand that all data has errors associated with it and we will ensure that these become encoded to allow
for additional optimizations. For example, all scientific simulations contain approximations, and all measurements from obervations and experiments 
also contain errors. These errors can help guide how information can be presented to users, by allowing us to ask for information within a given 
accuracy bound, and also allow us to offer a mode for recomputation vs. data storage and reterival.  
%
{\bf: please list other things from UCSC, OLCF}.
%

\underline{\textbf{Key Technical Approach:}}
%We are fundamentally trying to address the fundmantal questions : 1)  How can we 
%place and mangage massive scienfici data across all of the tiers of the storage and memory
%hiearchy? 2) What are the proper semantics needed in order to help bring knowledge from the applications
%to the middleware layer. 3) What information from the storage layer can be exposed to the middleweare such
%that the placement of information can be agreed upon from what the application requires and what the
%system resources are available.
